Bioinformatics analysis of whole-genome bisulfite-sequencing data

### 2015-05-05 Rmarkdown/wgbs_bioinformatics_analysis.Rmd
Polish methtuple performance plots

I have used `methtuple` to perform methylation calling at CpG m-tuples, $m = 1, \ldots, 8$, for $40$ whole-genome bisulfite-sequencing samples. Figure \ref{fig:methtuple_runtime} shows the distribution of running times and Figure \ref{fig:methtuple_memory} the maximum memory usage across all the samples from the EPISCOPE, Lister and Ziller datasets. For each sample, each chromosome was processed using a single core on one of the shared-use servers in the Bioinformatics Division (see Table \ref{tab:unices} in the Appendix for details of these machines).

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_runtime.pdf}
\caption[\texttt{methtuple} running time]{The running times are the `User time' reported by \texttt{GNU time} converted from seconds to minutes. The suffix `ac' on the tuple size means that the option \texttt{{-}{-}all-combinations} was set.}
\label{fig:methtuple_runtime}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_memory.pdf}
\caption[\texttt{methtuple} memory usage]{The maximum memory usage is the `Maximum resident set size' reported by \texttt{GNU time} converted from kilobytes to gigabytes. These values are divided by four to fix bug in how \texttt{GNU time} reports the maximum memory usage (\url{https://bugzilla.redhat.com/show_bug.cgi?id=703865}). The suffix `ac' means that the option \texttt{{-}{-}all-combinations} was set.}
\label{fig:methtuple_memory}
\end{figure}

>>>>

I have used `methtuple` to perform methylation calling at CpG m-tuples, $m = 1, \ldots, 8$, for more than $40$ whole-genome bisulfite-sequencing samples. Figure \ref{fig:methtuple_runtime} shows the distribution of running times and Figure \ref{fig:methtuple_memory} the maximum memory usage across all the samples from the EPISCOPE, Lister and Ziller datasets. For each sample, each chromosome was processed using a single core on one of the shared-use servers in the Bioinformatics Division (see Table \ref{tab:unices} in the Appendix for details of these machines).

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_runtime.pdf}
\caption[\texttt{methtuple} running time]{The running times are the `User time' reported by \texttt{GNU time} converted from seconds to minutes. The suffix `ac' on the tuple size means that the option \texttt{{-}{-}all-combinations} was set. Note that the total number of samples is $49$ because each of the Ziller sequencing runs is separetely counted (see Chapter \ref{chap:datasets} for details).}
\label{fig:methtuple_runtime}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/methtuple_memory.pdf}
\caption[\texttt{methtuple} memory usage]{The maximum memory usage is the `Maximum resident set size' reported by \texttt{GNU time} converted from kilobytes to gigabytes. These values are divided by four to fix bug in how \texttt{GNU time} reports the maximum memory usage (\url{https://bugzilla.redhat.com/show_bug.cgi?id=703865}). The suffix `ac' means that the option \texttt{{-}{-}all-combinations} was set. Note that the total number of samples is $49$ because each of the Ziller sequencing runs is separetely counted (see Chapter \ref{chap:datasets} for details).}
\label{fig:methtuple_memory}
\end{figure}
